Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-04 ms.tex
updated global parameter table values
outlining
more outlining and a bit of reorganizing

In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to 
isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
explain the dust emission model we fit to the \PLANCK~and \IRAS~data. In 
$\S$\ref{sec:global} we describe our constraints on this model's global 
parameters derived from the \PLANCK~High Frequency Instrument (HFI) maps. In 
$\S$\ref{sec:fitting} we detail the Markov chain Monte Carlo (MCMC) method with
which we have estimated the spatially varying parameters of our model. In 
$\S$\ref{sec:ebv} we calibrate our derived optical depth to reddening at 
optical wavelengths. In $\S$\ref{sec:results} we present the full-sky maps of 
dust temperature and optical depth we have obtained, and conclude in 
$\S$\ref{sec:conclusion}.

@@

\begin{deluxetable}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Model} &
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
 1 & FIRAS+\verb|i100| & 0.0363 & 13.0 & 1.67 & 2.70 \\
 2 & \PLANCK+\verb|i100| & 0.0267 & 3.68 & 1.19 & 2.61 \\ [-2ex]
\enddata
\end{deluxetable}

@@

\section{Calibrating to Optical Reddening}
\label{sec:ebv}

While the temperature and optical depth maps thus far derived are
useful for making thermal dust emission foreground predictions, estimating 
optical reddening/extinction is another important application of the 
$\tau_{545}$ map. We calibrate to reddening empirically rather than derive
a relationship between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution.

@@

To achieve this empirical calibration, we must adopt a set of calibrator
objects for which true optical reddening is known. There are various 
possibilities at our disposal. \cite{planckdust} calibrated their radiance 
and $\tau_{353}$ maps to $E(B-V)$ using broadband Sloan Digital Sky Survey 
\citep[SDSS;][]{sdss} photometry for a set of $\sim$10$^5$ quasars. The SFD 
calibration was originally tied to a sample of 384 elliptical galaxies, but was
later revised by \cite{schlafly11} using $\sim$250,000 stars with both 
spectroscopy and broadband photometry available from SDSS. To calibrate our 
$\tau_{545}$ to reddening, we make use of the same set of stars studied by 
\cite{schlafly11}.

@@

@@

\section{Results}
\label{sec:results}

\subsection{Data Release}
We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
summarizing the results of of our two-component dust fits.

@@

\subsection{Comparison to Planck Collaboration Dust Map}
%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
An important difference between our maps and those of \cite{planckdust} is our 
use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
clearly visible in the \cite{planckdust} maps.

\section{Conclusion}

% should mention that one definitive improvement of this work relative
% to FDS99 is that there are uncertainty/covariances provided for
% the derived parameters !!!!

\label{sec:conclusion}

@@

>>>>

In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to 
isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
explain the dust emission model we fit to the \PLANCK~and \IRAS~data. In 
$\S$\ref{sec:global} we describe our constraints on this model's global 
parameters derived from the \PLANCK~High Frequency Instrument (HFI) maps. In 
$\S$\ref{sec:fitting} we detail the Markov chain Monte Carlo (MCMC) method with
which we have estimated the spatially varying parameters of our model. In 
$\S$\ref{sec:ebv} we calibrate our derived optical depth to reddening at 
optical wavelengths. In $\S$\ref{sec:release} we present the full-sky maps of 
dust temperature and optical depth we have obtained, and conclude in 
$\S$\ref{sec:conclusion}.

@@

\begin{deluxetable}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Model} &
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
 1 & FIRAS+\verb|i100| & 0.0363 & 13.0 & 1.67 & 2.70 \\
 2 & \PLANCK+\verb|i100| & 0.0485 & 8.22 & 1.63 & 2.82 \\ [-2ex]
\enddata
\end{deluxetable}

@@

\subsection{Global Parameters Revisited}
% discuss goodness of fit tests based on running Markov chains with different
% sets of global parameters

\section{Optical Reddening}
\label{sec:ebv}

While the temperature and optical depth maps thus far derived are
useful for making thermal dust emission foreground predictions, estimating 
optical reddening/extinction is another important application of the 
$\tau_{545}$ map.

\subsection{Reddening Calibration Procedure}

@@

We calibrate to reddening empirically rather than derive
a relationship between $\tau_{545}$ and reddening by introducing additional 
assumptions about the dust grain physics and size distribution. To achieve this
empirical calibration, we must adopt a set of calibrator objects for which true
optical reddening is known. There are various possibilities at our disposal. 
\cite{planckdust} calibrated their radiance and $\tau_{353}$ maps to $E(B-V)$ 
using broadband Sloan Digital Sky Survey \citep[SDSS;][]{sdss} photometry for a
set of $\sim$10$^5$ quasars. The SFD calibration was originally tied to a 
sample of 384 elliptical galaxies, but was later revised by \cite{schlafly11} 
using $\sim$250,000 stars with both spectroscopy and broadband photometry 
available from SDSS. To calibrate our $\tau_{545}$ to reddening, we make use of
the same set of stars studied by \cite{schlafly11}.

@@

\subsection{Rectifying Reddening Residuals}
% discuss changing global params and offsets, and ecl plane cut

@@

\section{Low-frequency Emission Predictions}
% compare 100-217 GHz predictions using my model versus Planck Collaboration
% single-MBB model

% is this the section where, potentially, plots of the residuals might go?

%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
An important difference between our maps and those of \cite{planckdust} is our 
use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
clearly visible in the \cite{planckdust} maps.

\section{Data Release}
\label{sec:release}
We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
summarizing the results of of our two-component dust fits.

@@

@@

\section{Conclusions}
\label{sec:conclusion}
% should mention that one definitive improvement of this work relative
% to FDS99 is that there are uncertainty/covariances provided for
% the derived parameters !!!!
